Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-06-25 Journal1/paper-version3-TNSM/pr.tex
add sth

If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{s}^\text{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$. Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
\subsection{Power of the O-RU and the Fronthaul Capacity}
Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to all the UEs served by it. From \eqref{eq2}, the power of each O-RU $r$ is obtained as follows, 
%{\color{red} is this the sum rate of all users?}
\begin{equation}\label{pr}
P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q}^2.
\end{equation}
Since we have a fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
%\cite{simeone2016cloud, 1111}
\begin{equation}\label{cr}
C_{r} = \log{\left(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2}\right)},
\end{equation}
where $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q}^2$ is the power of quantization noise.
\subsection{Mean Delay}
In this part, the end-to-end mean delay for each service is obtained.
Suppose the mean total delay is depicted as $T_{\text{\text{tot}}}$,
\begin{subequations}
\begin{alignat}{4}
T^{\text{\text{tot}}} &=  T^{\text{proc}} + T^{tr} + T^{\text{pro}},\\
T^{\text{\text{proc}}} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF},\\
T^{tr} &= T^{fr,t} + T^{\text{mid},t} + T^{b,t},  \\
T^{\text{pro}} &= T^{fr,p} + T^{\text{mid},p} + T^{b,p}. 
\end{alignat}
\end{subequations}
%{\color{red} I made a mistake and replaced pro with proc. Please correct them. Also, explain in more details the processing delay in this paragraph.}
%T_{\text{\text{tot}}} = T_{RU} + T_{front} + T_{DU} + T_{\text{mid}} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
The total delay ($T^{\text{\text{tot}}}$), is the sum of the processing delay ($T^{\text{proc}}$), the transmission delay ($T^{tr}$), and the propagation delay ($T^{\text{pro}}$). 
The propagation delay is the time takes for a signal to reach its destination. It obtains based on the length of the fiber link and the capacity of the link ($T = L/c$, where $L$ is the length of the link and c is the propagation speed of the link). The total propagation delay ($T^{\text{pro}}$), is the sum of the propagation delay in the fronthaul link $T^{fr,p}$, the midhaul link $T^{\text{mid},p}$, and the backhaul link $T^{b,p}$.
Also, the transmission delay is the amount of time required to push all the packets into the fiber link.
Moreover, it can formulated as 
$T = \frac{\mathcal{\alpha}}{R}$, where $R$ is the data-rate of the packet transmission in each link and $\mathcal{\alpha}$ is the mean packet size transmitting in each link.
So the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{\text{mid},t}$, and the backhaul $T^{b,t}$.

@@

\textcolor{MidnightBlue}{A significant issue facing the industry is reducing energy consumption. Data centers are one of the most energy-consuming. As a result, restrictions are placed on data centers' energy, including virtual machines (VMs). So, one of our goals is to limit the energy consumption of total VNFs that can be run as VM on data centers. So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^\text{max}$).}

@@

\text{subject to} \quad  &  P_r \leq P^\text{max}_{r} \quad \forall r

@@

&p_{r,u(s,i)}^{k}  \leq P_{s}^\text{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\
&\bar{\mathcal{R}}_{u_{(s,i)}} \geq \mathcal{R}_{{s}}^{\min} \quad \forall s, \label{c13} \\

@@

& C_r \leq C^\text{max}_r \quad \forall r, \label{c15}\\ 
&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^\text{max}_{s} \quad \forall i,\forall s,\label{c16} \\

@@

& 0 \leq M_s \leq M^\text{max}_s  \quad \forall s,\label{c16-3}\\
& \phi^{\text{\text{tot}}}  \leq \phi^\text{max}, \label{c19} \\

@@

Suppose, $\mathcal{R}_{{s}}^{\min}$, and $\mathcal{R}_{{s}}^\text{max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.

@@

So, the minimum number of PRB that slice s with $U_s$ UEs requires is $K_s^{\min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^\text{max}}}\rceil$. $K_s^{\min} $ is the minimum number of PRBs needed for slice s, and K is the total number of PRBs in the system.  
Moreover, the maximum number of PRB that slice s with $U_s$ UEs requires is $K_s^\text{max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{\min}}}\rceil$. $K_s^\text{max} $ is the maximum number of PRBs needed for slice s, and K is the total number of PRBs in the system. Also, $K_s = (K_s^{\min}+K_s^\text{max})/2$ is the average number of required PRB in slice s (eMBB slice).

@@

& K_s^{\min} \leq \bar{K_s}  \leq K_s^\text{max}  \quad \forall s \in S_1,\label{prb1} \\

@@

In the preparation phase, the evaluation of requirements is considered. After that, we use our algorithm to find the optimal number of VNFs for each slice and PRB assignment and power allocation. Therefore, in the preparation phase, we estimate our resource of slices, and in the commission phase, we allocate our resources to the slices.
%\vspace*{-1em}
\section{Proposed Algorithm}\label{proAlg}
In this section, we first apply some simplifications to the system; Solving the problem \eqref{problem} is complicated since this is non-convex mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable. 
We applied some simplifications and use an iterative heuristic algorithm to solve the problem.
We solve this problem in two levels, iteratively, until it converges \cite{ali2018joint}.

@@

\subsection{Sub-Problem 1}\label{sub1}
Suppose that $\boldsymbol{G}$ is fixed, we want to obtain $\boldsymbol{P}, \boldsymbol{E}$ and $\boldsymbol{M}$.
Here, we first simplify and relax the parameters to convexify the problem.
As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} with $P^\text{max}_s$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$, and also the lower bound $\bar{\rho}_{u(s,i)}^{k}$ is achieved
for $\rho_{u(s,i)}^{k}$. 
Moreover, the lower bound $\bar{\mathcal{R}}_{u_{(s,i)}}, \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing $I_{r,u(s,i)}^{k}$ with $\bar{I}_{r,u(s,i)}^{k}$ in \eqref{eq11} and \eqref{eq3} and make these equations become concave functions.

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^\text{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
So, a lower bound for \eqref{eq11} is given that is a concave function.
\begin{subequations}\label{lb1}
\begin{alignat}{4}
\bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r}\\ 
 \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
 \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}.
\end{alignat}
\end{subequations}
Without loss of generality, assume that UPF, O-CU and O-DU use the processors with the same processing capability. We notice that it makes the formulation simpler. However, loosing this assumption does not change the formulation significantly and the problem can be solved in the same manner. Therefore, we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). So $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. Again, this assumption only simplifies the notations and loosing it does not make the solution inefficient.
These assumptions lead to having the same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
As a result, we have $M_s = M_s^u = M_s^c = M_s^d $.
Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ and we have 
$T^{\text{proc}}_{s} =  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}$. So,
$T^{\text{proc}}_{s}=  T^{RU}_{s} + 3\times T^{DU}_{s}.$  
%\begin{equation}
%\begin{split}
%T^{\text{proc}}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
%                     &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
%\end{split}
%\end{equation}

@@

where, $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^\text{max}_s R_{u(s,i)}-T^\text{max}_s\lambda_{u(s,i)} -1)}{(T^\text{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.

@@

We denote $ \mathfrak{M}_s= \min\{M^\text{max}, \phi_{\max}/{3\phi_s}\}$.

@@

\alpha_s/\mu_s\leq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s

@@

In equation \eqref{eqDelay}, $0\leq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that 

@@

If we assume that the $(R_{u(s,i)}-\lambda_{u(s,i)})T^{\max}_s \geq 1$, the numerator will be positive.
$(R_{u(s,i)}-\lambda_{u(s,i)})T^{\max}_s \geq 1$ since the order of $T^{\max}_s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T^{\max}_s$.
Therefore, to ensure that this constraint will be valid, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T^{\max}_s$.

@@

In the denominator, we can say that $(T^{\max}_s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since,  

@@

$(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T^{\max}_s$ as mentioned above.

@@

\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{\max}_s}\\
& + \frac{3}{T^{\max}_s\mu_s-\alpha_s T^{\max}_s/\mathfrak{M}_s-3}

@@

In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.

@@

 $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{\max}}$.

@@

\zeta_{r}&= \min\{P_{\max}, \sigma_{q_r}^2\times 2^{C^r_{\max}} \}, \\

@@

&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{q}^k_{r,u(s,i)} (P^{\max}_{s}- p^k_{r,u(s,i)})\\

@@

 \begin{algorithm}
 \small
\caption{Iterative algorithm for the baseband resource allocation and VNF activation (IABV)}\label{alg2}
\begin{algorithmic}[1]
\State  Set the maximum number of iterations ${Iter}_{\max}$, convergence condition $\epsilon > 0$ \label{a21}
\State  Assign Users to O-RU randomly (Initialize $\boldsymbol{G}$) \label{a22}
\For {$i \gets 1$ to $Iter_{\max}$}\label{23}
\State Acquire $\boldsymbol{P}^{(i)}$, $\boldsymbol{E}^{(i)}$ and $\boldsymbol{M}^{(i)}$ using Lagrangian function and sub-gradient method based on \eqref{sub1}
\State Update $\boldsymbol{G}^{(i)}$   based on algorithm GAAOU \eqref{alg1} in  \eqref{sub2}
\If {the algorithm converged with the tolerence of $\epsilon$}
\State Break
\Else 
\State Continue the algorithm  
\EndIf
\State \textbf{end if}
\EndFor
\State \textbf{end for} \label{24}
\end{algorithmic}
\end{algorithm} 
\subsection{Iterative Proposed Algorithm}
In Sections \eqref{sub1} and \eqref{sub2}, the details of solving each sub-problem are depicted. 
Here, the iterative algorithm for the whole problem is demonstrated.
Firstly, we fixed $\boldsymbol{G}$ to achieve $\boldsymbol{P}$ and $\boldsymbol{E}$, using the Lagrangian method and the KKT conditions.  
Afterward, $\boldsymbol{G}$ is updated using the GAA algorithm. This process is repeated until it converges. 
The whole algorithm (IABV method) is depicted as follows (Algorithm \ref{alg2}).

@@

and we suppose that each UE has the maximum power $p_{r,u_{(s,i)}}^k = P_{s}^{\max}$,

@@

and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{\max}/100$. \textcolor{MidnightBlue}{The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.}

>>>>

If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{s}^{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$. Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
\subsection{Power of the O-RU and the Fronthaul Capacity}
Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to all the UEs served by it. From \eqref{eq2}, the power of each O-RU $r$ is obtained as follows, 
%{\color{red} is this the sum rate of all users?}
\begin{equation}\label{pr}
P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q}^2.
\end{equation}
Since we have a fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
%\cite{simeone2016cloud, 1111}
\begin{equation}\label{cr}
C_{r} = \log{\left(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2}\right)},
\end{equation}
where $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q}^2$ is the power of quantization noise.
\subsection{Mean Delay}
In this part, the end-to-end mean delay for each service is obtained.
Suppose the mean total delay is depicted as $T_{\text{\text{tot}}}$,
\begin{subequations}
\begin{alignat}{4}
T^{\text{\text{tot}}} &=  T^{\text{proc}} + T^{tr} + T^{\text{pro}},\\
T^{\text{\text{proc}}} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF},\\
T^{tr} &= T^{fr,t} + T^{\text{mid},t} + T^{b,t},  \\
T^{\text{pro}} &= T^{fr,p} + T^{\text{mid},p} + T^{b,p}. 
\end{alignat}
\end{subequations}
%{\color{red} I made a mistake and replaced pro with proc. Please correct them. Also, explain in more details the processing delay in this paragraph.}
%T_{\text{\text{tot}}} = T_{RU} + T_{front} + T_{DU} + T_{\text{mid}} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
The total delay ($T^{\text{\text{tot}}}$), is the sum of the processing delay ($T^{\text{proc}}$), the transmission delay ($T^{tr}$), and the propagation delay ($T^{\text{pro}}$). 
The propagation delay is the time takes for a signal to reach its destination. It obtains based on the length of the fiber link and the capacity of the link ($T = L/c$, where $L$ is the length of the link and c is the propagation speed of the link). The total propagation delay ($T^{\text{pro}}$), is the sum of the propagation delay in the fronthaul link $T^{fr,p}$, the midhaul link $T^{\text{mid},p}$, and the backhaul link $T^{b,p}$.
Also, the transmission delay is the amount of time required to push all the packets into the fiber link.
Moreover, it can formulated as 
$T = \frac{\mathcal{\alpha}}{R}$, where $R$ is the data-rate of the packet transmission in each link and $\mathcal{\alpha}$ is the mean packet size transmitting in each link.
So the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{\text{mid},t}$, and the backhaul $T^{b,t}$.

@@

\textcolor{MidnightBlue}{A significant issue facing the industry is reducing energy consumption. Data centers are one of the most energy-consuming. As a result, restrictions are placed on data centers' energy, including virtual machines (VMs). So, one of our goals is to limit the energy consumption of total VNFs that can be run as VM on data centers. So, by applying a custom policy on total power consumption, we can control data centers' power consumption ($\phi^{\text{\text{tot}}}  \leq \phi^{max}$).}

@@

\text{subject to} \quad  &  P_r \leq P^{max}_{r} \quad \forall r

@@

&p_{r,u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\
&\bar{\mathcal{R}}_{u_{(s,i)}} \geq \mathcal{R}_{{s}}^{min} \quad \forall s, \label{c13} \\

@@

& C_r \leq C^{max}_r \quad \forall r, \label{c15}\\ 
&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i,\forall s,\label{c16} \\

@@

& 0 \leq M_s \leq M^{max}_s  \quad \forall s,\label{c16-3}\\
& \phi^{\text{\text{tot}}}  \leq \phi^{max}, \label{c19} \\

@@

Suppose, $\mathcal{R}_{{s}}^{min}$, and $\mathcal{R}_{{s}}^{max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.

@@

So, the minimum number of PRB that slice s with $U_s$ UEs requires is $K_s^{min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{max}}}\rceil$. $K_s^{min} $ is the minimum number of PRBs needed for slice s, and K is the total number of PRBs in the system.  
Moreover, the maximum number of PRB that slice s with $U_s$ UEs requires is $K_s^{max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}}\rceil$. $K_s^{max} $ is the maximum number of PRBs needed for slice s, and K is the total number of PRBs in the system. Also, $K_s = (K_s^{min}+K_s^{max})/2$ is the average number of required PRB in slice s (eMBB slice).

@@

& K_s^{min} \leq \bar{K_s}  \leq K_s^{max}  \quad \forall s \in S_1,\label{prb1} \\

@@

%\vspace*{-1em}
\section{Proposed Algorithm}\label{proAlg}
In this section, we first apply some simplifications to the system; Solving the problem \eqref{problem} is complicated since this is non-convex mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable. 
We applied some simplifications and use an iterative heuristic algorithm to solve the problem.
We solve this problem in two levels, iteratively, until it converges \cite{ali2018joint}.

@@

\subsection{Sub-Problem 1}\label{sub1}
Suppose that $\boldsymbol{G}$ is fixed, we want to obtain $\boldsymbol{P}, \boldsymbol{E}$ and $\boldsymbol{M}$.
Here, we first simplify and relax the parameters to convexify the problem.
As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} with $P^{max}_s$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$, and also the lower bound $\bar{\rho}_{u(s,i)}^{k}$ is achieved
for $\rho_{u(s,i)}^{k}$. 
Moreover, the lower bound $\bar{\mathcal{R}}_{u_{(s,i)}}, \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing $I_{r,u(s,i)}^{k}$ with $\bar{I}_{r,u(s,i)}^{k}$ in \eqref{eq11} and \eqref{eq3} and make these equations become concave functions.

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
So, a lower bound for \eqref{eq11} is given that is a concave function.
\begin{subequations}\label{lb1}
\begin{alignat}{4}
\bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r}\\ 
 \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
 \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}.
\end{alignat}
\end{subequations}
Without loss of generality, assume that UPF, O-CU and O-DU use the processors with the same processing capability. We notice that it makes the formulation simpler. However, loosing this assumption does not change the formulation significantly and the problem can be solved in the same manner. Therefore, we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). So $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. Again, this assumption only simplifies the notations and loosing it does not make the solution inefficient.
These assumptions lead to having the same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
As a result, we have $M_s = M_s^u = M_s^c = M_s^d $.
Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ and we have 
$T^{\text{proc}}_{s} =  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}$. So,
$T^{\text{proc}}_{s}=  T^{RU}_{s} + 3\times T^{DU}_{s}.$  
%\begin{equation}
%\begin{split}
%T^{\text{proc}}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
%                     &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
%\end{split}
%\end{equation}

@@

where, $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.

@@

We denote $ \mathfrak{M}_s= \min\{M^{max}, \phi_{max}/{3\phi_s}\}$.

@@

\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s

@@

In equation \eqref{eqDelay}, $0\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that 

@@

If we assume that the $(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$, the numerator will be positive.
$(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$ since the order of $T^{max}_s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T^{max}_s$.
Therefore, to ensure that this constraint will be valid, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T^{max}_s$.

@@

In the denominator, we can say that $(T^{max}_s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since,  

@@

$(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T^{max}_s$ as mentioned above.

@@

\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s}\\
& + \frac{3}{T^{max}_s\mu_s-\alpha_s T^{max}_s/\mathfrak{M}_s-3}

@@

In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.

@@

 $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{max}}$.

@@

\zeta_{r}&= min\{P_{max}, \sigma_{q_r}^2\times 2^{C^r_{max}} \}, \\

@@

&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{q}^k_{r,u(s,i)} (P^{max}_{s}- p^k_{r,u(s,i)})\\

@@

 \begin{algorithm}
 \small
\caption{Iterative algorithm for the baseband resource allocation and VNF activation (IABV)}\label{alg2}
\begin{algorithmic}[1]
\State  Set the maximum number of iterations ${Iter}_{max}$, convergence condition $\epsilon > 0$ \label{a21}
\State  Assign Users to O-RU randomly (Initialize $\boldsymbol{G}$) \label{a22}
\For {$i \gets 1$ to $Iter_{max}$}\label{23}
\State Acquire $\boldsymbol{P}^{(i)}$, $\boldsymbol{E}^{(i)}$ and $\boldsymbol{M}^{(i)}$ using Lagrangian function and sub-gradient method based on \eqref{sub1}
\State Update $\boldsymbol{G}^{(i)}$   based on algorithm GAAOU \eqref{alg1} in  \eqref{sub2}
\If {the algorithm converged with the tolerence of $\epsilon$}
\State Break
\Else 
\State Continue the algorithm  
\EndIf
\State \textbf{end if}
\EndFor
\State \textbf{end for} \label{24}
\end{algorithmic}
\end{algorithm} 
\subsection{Iterative Proposed Algorithm}
In Sections \eqref{sub1} and \eqref{sub2}, the details of solving each sub-problem are depicted. 
Here, the iterative algorithm for the whole problem is demonstrated.
Firstly, we fixed $\boldsymbol{G}$ to achieve $\boldsymbol{P}$ and $\boldsymbol{E}$, using the Lagrangian method and the KKT conditions.  
Afterward, $\boldsymbol{G}$ is updated using the GAA algorithm. This process is repeated until it converges. 
The whole algorithm (IABV method) is depicted as follows (Algorithm \ref{alg2}).

@@

and we suppose that each UE has the maximum power $p_{r,u_{(s,i)}}^k = P_{s}^{max}$,

@@

and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. \textcolor{MidnightBlue}{The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.}
